Evaluating polarizable biomembrane simulations against experiments

### 2023-12-01 manuscriptPOL.tex

\author{Hanne Antila}
\author{Batuhan Kav}
\affiliation{Forschungszentrum Juelich, Germany}
\email{batuhankav@gmail.com}
\author{Jesper J. Madsen}
\author{Markus S. Miettinen}
\author{O. H. Samuli Ollila}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\title[An \textsf{achemso} demo]
%  {A demonstration of the \textsf{achemso} \LaTeX\
%   class\footnote{A footnote for the title}}
%\title{NMRLipids VI: Polarizable Force Fields}
\title{Do explicitly polarizable force fields give better description of biomembranes?}
%\title{Comparison of polarizable lipid models to high-resolution experimental data reveals room for improvement}
%\title{Benchmarking polarizable lipid force field}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\abbreviations{IR,NMR,UV}
%\keywords{American Chemical Society, \LaTeX}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
With the increase of available computational capabilities, polarizable molecular dynamics force fields have gained popularity in modelling biomolecular systems. In the case of biomembranes in particular, they are expected to provide better description, eg., by capturing the varying dielectric environment across the lipid bilayer. Here, we use the framework established within the NMRlipids open science project and the related NMRlipids databank to test the commonly used polarizable lipid models, CHARMM-Drude and AMOEBA, against high fidelity experimental data and best non-polarizable models. 
%We find that, for each property tested, the best non-polarizable models surpass the polarizable ones. The flaws detected range from inaccuracies in describing the conformational space of lipid tails (AMOEBA) to the drastically too slow conformational dynamics of CHARMM-Drude models. That said, there is no model, polarizable or non-polarizable, that is consistently the best across all the properties tested.

@@

In conventional molecular dynamics (MD) simulations, electrostatic interactions are described by assigning static point charges to the atoms and molecules at the beginning of the simulation as defined in the inputted model---the force field. Dynamic effects arising from molecular polarizability are traditionally not explicitly included and only considered in an averaged fashion via force field parameterization process where parameters are obtained by fitting to macroscopic observables or to ab initio calculations. Significant efforts have been dedicated to introduce explicit polarizability into MD simulations, in the hopes of reaching a more accurate representation of the system~\cite{Thole1981,ando2001stable,Grossfield2003,
lamoreux2003,Antila2013 ,Lemkul2016, baker2015polarizable,jing2019polarizable }. This effort has been motivated by the plethora of interactions where polarization is perceived to be a key contribution to correctly describing the system. These include description of water, ion hydration and ion binding to molecules, cation--$\pi$ and $\pi$-$\pi$ interactions~\cite{inakollu2020polarisable}. These lower-level interactions also translate to the behaviour of larger-scale biological systems, such as ion channels, where ion-selectivity and ion currents may be affected by polarization~\cite{roux2011ion, klesse2020induced, prajapati2020computational,Yue2022}, and telomeric DNA~\cite{Salsbury22} where the conformations adopted are mediated by ionic interactions.

For bilayer membrane simulation, specifically,  the molecular (dielectric) environment varies dramatically while crossing the membrane from the water phase across the dipolar/charged lipid headgroup interface to the hydrophobic tail region. Therefore, including polarizability in the lipids is expected to provide more accurate description, especially in situations pertaining to membrane binding processes, membrane potential and translocation of charged biomolecules across the membrane, and the behavior of molecules residing within membranes, such as membrane proteins~\cite{baker2015polarizable,Lemkul2016, li2017drude,chu2018anionicpolarizable,Lynch21,Chen2021,Melcr:2018a, melcr2019improved,nencini22}.

The available lipid force fields with explicit electronic polarization include CHARMM-Drude~\cite{li2017drude, yu2023drude}, AMOEBA~\cite{chu2018anionicpolarizable,chu2018polarizable}, and CHARMM-Fluctuating Charge (FQ)~\cite{lucas2012charge}. The underlying strategy for including explicit polarizability differ among these models:  1) the classical Drude oscillator (CHARMM-Drude) models polarization by separating a core and a shell charge with a spring which stretches according to the environment giving the site a fluctuating dipole moment~\cite{Lemkul2016},
2) the induced point dipole/multipole (AMOEBA) uses polarizable point dipoles placed on chosen sites of the molecule~\cite{ponder2010current},
and 3) the electronegativity equilization (FQ) employs atomic charges that are no longer constant but can change (redistribute within the molecule) according to the electronegativities of the molecule atoms and the electric fields from the molecular environment~\cite{patel2004charmm}. All of these approaches result in an increasing computational cost, e.g, by introducing new types of interactions, more interactions sites, or by requiring a shorter time step in the simulations. As an alternative approach, electronic continuum correction (ECC) has been proposed as a computational efficient method to implicitly include polarizability by scaling the atom partial charges~\cite{Melcr:2018a,dijon20}.

%Hence, there certainly is room for improvement: efforts from the NMRlipids open science community have shown that the current non-polarizable lipid models cannot correctly reproduce the conformational ensemble~\cite{Botan2015,Antila2019}, conformational dynamics~\cite{Antila2021}, or ion biding~\cite{Catte2016} within MD simulations.

Our previous efforts in benchmarking state-of-the-art non-polarizable lipid force fields have demonstrated that the quality of predictions for important membrane properties greatly vary between different force fields, particularly for lipid headgroup conformational ensembles and ion binding affinities~\cite{Botan2015,Catte2016,Antila2019,bacle21,Antila2021,Antila2022,Databank}. The ability to capture these membrane properties correctly is important on its own but also creates the basis for the description of more complex systems: for example, ion binding affinity regulates membrane surface charge and wide variety of conformations available for lipid headgroups appears to be important for modeling realistic protein-lipid binding~\cite{bacle21}. Therefore, such benchmark studies are urgently needed also for polarizable lipid force fields, considering  the increased computational cost they come with, and most importantly, their pledge
%important when employing polarizable force fields, as they offer the potential 
to capture a broader range of physical phenomena pertinent to enhancing our understanding of in particular polar membrane regions.

Here we assess the quality of actively developed polarizable lipid force fields, CHARMM-Drude~\cite{li2017drude,yu2023drude} and  AMOEBA~\cite{chu2018anionicpolarizable,chu2018polarizable}, using the resources and the framework from the NMRLipids open collaboration (\url{http://nmrlipids.blogspot.fi/}). These two force fields were selected for comparison because they are increasingly utilized in biomolecular simulations and have parameters available for several lipids for which corresponding experimental data is available in NMRlipids databank~\cite{Databank}. We assess the structural quality of POPC, DOPC and POPE lipid bilayer simulations against experimental NMR and small angle X-ray scattering (SAXS) data using the quality metrics defined in the NMRlipids databank~\cite{Databank}. Cation binding to membranes was evaluated against NMR order parameters~\cite{Catte2016} and lipid conformational dynamics is benchmarked to data from NMR spin relaxation rate experiments~\cite{ferreira15,Antila2021}. 
Furthermore, for each experimental benchmark we compare the results from polarizable models to those from the best performing non-polarizable simulations obtained from the NMRlipids Databank\cite{Databank}.

%All simulation data, analysis scripts, and results are publicly available in their corresponding links. No plausible nor implausible request is required to download, use, and disseminate the data.

@@

To evaluate the structural properties of lipid bilayers in simulations with polarizable force fields, we simulated POPC and POPE lipid bilayers with CHARMM-Drude2017~\cite{li2017drude} and CHARMM-Drude2023~\cite{yu2023drude} parameters, and POPE and DOPC bilayers with AMOEBA~\cite{chu2018anionicpolarizable,chu2018polarizable} parameters. These systems were selected based on simultaneous availability of force field parameters, and experimental data~\cite{Databank}. After the data production, simulation trajectories were added into the NMRlipids Databank and its quality metrics was used to evaluate each simulation against experiments~\cite{Databank}. This metric measures the quality of lipid bilayer simulations in two aspects: first, it evaluates the quality of conformational ensemble of individual lipids against C-H bond order parameters from NMR, and second, it examines consistency of membrane dimensions compared to small angle X-ray scattering (SAXS) data~\cite{Databank,ollila16}. 
%(measuring the electron density variation across the membrane). 
The former is divided into three parts that separately describe the average quality of headgroup, glycerol backbone and acyl chain qualities as described in the NMRlipids databank~\cite{Databank}. While order parameters primarily reflect lipid conformations, acyl chain order parameters are also a good proxy for membrane packing since a smaller area per lipid tends to increase the magnitude of the order parameters~\cite{Databank}. 
%one for each of the carbonyl tails, and the quality of each is evaluated separately.

\begin{figure}[t]
    \centering
    %\includegraphics{Figures/order_parameters.png}
    \includegraphics[width=0.4\textwidth]{Figures/molecules.pdf}
    \caption{Molecules and atom labelling used.}
    \label{fig:molecules}

@@

\section{Supplementary figures}

\begin{figure}[!h]
    \centering
    %\includegraphics{Figures/order_parameters.png}
    \includegraphics[width=0.8\textwidth]{Figures/quality_Drude2023_replicas.pdf}
    \caption{X-ray scattering form factors, and C-H bond order parameters for headgroup and glycerol backbone, and acyl chains (from top to bottom) compared between simulations and experiments using the NMRlipids databank. The atom labelling is as depicted in Fig.~\ref{fig:molecules}.}
    \label{fig:order_parameters_replicas}

>>>>

\author{Hanne S. Antila}
\affiliation{Department of Theory and Bio-Systems, Max Planck Institute of Colloids and Interfaces, 14476 Potsdam, Germany}
\alsoaffiliation{Department of Biomedicine, University of Bergen, 5020 Bergen, Norway}
\email{hanne.antila@uib.no}
\author{Sneha Dixit}
\affiliation{Department of Theory and Bio-Systems, Max Planck Institute of Colloids and Interfaces, 14476 Potsdam, Germany}
\author{Batuhan Kav}
\affiliation{Forschungszentrum Juelich, Germany}
\email{batuhankav@gmail.com}
\author{Jesper J. Madsen}
\affiliation{Department of Molecular Medicine, Morsani College of Medicine, University of South Florida, Tampa, Florida 33612, United States of America}
\alsoaffiliation{Center for Global Health and Infectious Diseases Research, Global and Planetary Health, College of Public Health, University of South Florida, Tampa, Florida 33612, United States of America}
\author{Markus S. Miettinen}
\author{O. H. Samuli Ollila}
\affiliation{VTT Technical Research Centre of Finland, Espoo, Finland}
\alsoaffiliation{Institute of Biotechnology, University of Helsinki, Helsinki, Finland}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\title[An \textsf{achemso} demo]
%  {A demonstration of the \textsf{achemso} \LaTeX\
%   class\footnote{A footnote for the title}}
%\title{NMRLipids VI: Polarizable Force Fields}
%\title{Do explicitly polarizable force fields give better description of biomembranes?}
%\title{Comparison of polarizable lipid models to high-resolution experimental data reveals room for improvement}
%\title{Benchmarking polarizable lipid force field}
\title{Evaluating polarizable biomembrane simulations against experiments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\abbreviations{IR,NMR,UV}
%\keywords{American Chemical Society, \LaTeX}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%Classical molecular dynamics (MD) simulations are powerful tool to model membranes and other complex biomolecular systems with high spatiotemporal resolution. However, conventional MD simulations assume static point charges to the atoms, thereby neglecting the electronic polarizability effects. Because electronic polarization effects play key roles in many biomolecular systems, 
%. With the remarkable advances in available computational capabilities, 
%polarizable molecular dynamics force fields are gaining popularity for more accurate modeling of biomolecular systems. For these advances, it is crucial to evaluate how accuracy of models against experiments evolves when computational cost and complexity of simulations are increasing.

%Notably, in the context of biomembranes, these force fields  are expected to offer an improved description, eg., by more accurately capturing the dynamic dielectric environment across the lipid bilayer. 
Owing to the increase of available computational capabilities and the potential for providing more accurate description, polarizable molecular dynamics force fields are gaining popularity in modelling biomolecular systems. It is, however, crucial to evaluate how much precision is truly gained with the increased cost and complexity of the simulation. Here, we leverage the NMRlipids open collaboration and databank to assess the performance available polarizable lipid models, CHARMM-Drude and AMOEBA-based parameters, against high-fidelity experimental data and compare them to top-performing non-polarizable models. While some improvement in description of ion binding to membranes is observed in the most recent CHARMM-Drude parameters, and the conformational dynamics of AMOEBA-based parameters are excellent, best non-polarizable models tend to outperformed their polarizable counterparts for each property we explored. The identified shortcomings range from inaccuracies in describing the conformational space of lipids to excessively slow conformational dynamics. Our results provide valuable insights
for further refinement of polarizable lipid force fields and for selecting the best simulation parameters for specific applications. 
%We find that, for each property tested, the best non-polarizable models surpass the polarizable ones. The flaws detected range from inaccuracies in describing the conformational space of lipid tails (AMOEBA) to the drastically too slow conformational dynamics of CHARMM-Drude models.  That said, there is no model, polarizable or non-polarizable, that is consistently the best across all the properties tested.

@@

Classical molecular dynamics (MD) simulations are nowadays widely and almost routinely used to model wide range of biomolecular complexes~\cite{gupta22}. In conventional MD simulations, electrostatic interactions are described by assigning static point charges to the atoms and molecules at the beginning of the simulation as defined in the inputted model---the force field. Dynamic effects arising from electronic polarizability are traditionally not explicitly included and only considered in an averaged fashion within the force field parameterization process where parameters are obtained by fitting to macroscopic observables or to \textit{ab initio} calculations. However, electronic polarization is perceived to be a key contribution to correctly describe many biomolecular systems. These include description of water, ion hydration and ion binding to molecules, cation--$\pi$ and $\pi$-$\pi$ interactions~\cite{inakollu2020polarisable}, and general co-operativity in interactions~\cite{nochebuena23}. These lower-level interactions also translate to the behaviour of larger-scale biomolecular systems, such as ion channels, where ion-selectivity and ion currents may be affected by polarization~\cite{roux2011ion, klesse2020induced, prajapati2020computational,Yue2022}, and telomeric DNA~\cite{Salsbury22} where the conformations adopted are mediated by ionic interactions. Therefore, significant efforts have been dedicated to introduce explicit polarizability into MD simulations in the hopes of reaching a more accurate representation of the system~\cite{Thole1981,ando2001stable,Grossfield2003,lamoreux2003,Antila2013,Lemkul2016,baker2015polarizable,jing2019polarizable}.

In a bilayer membrane, specifically, the molecular (dielectric) environment varies dramatically while crossing the membrane from the water phase across the dipolar/charged lipid headgroup interface to the hydrophobic tail region. Therefore, including polarizability in the lipids is expected to provide more accurate description, especially in situations pertaining to membrane binding processes, membrane potential and translocation of charged biomolecules across the membrane, and the behavior of molecules residing within membranes, such as membrane proteins~\cite{baker2015polarizable,Lemkul2016, li2017drude,chu2018anionicpolarizable,Lynch21,Chen2021,Melcr:2018a, melcr2019improved,nencini22}. However, the quality of polarizable lipid models have not been evaluated on an equal footing with non-polarizable models.

The available lipid force fields with explicit electronic polarization include CHARMM-Drude~\cite{li2017drude, yu2023drude}, AMOEBA-based~\cite{chu2018anionicpolarizable,chu2018polarizable}, and CHARMM-Fluctuating Charge (FQ)~\cite{lucas2012charge} parameters. The underlying strategy for including explicit polarizability differ among these models:  1) the classical Drude oscillator (CHARMM-Drude) models polarization by separating a core and a shell charge with a spring which stretches according to the environment giving the site a fluctuating dipole moment~\cite{Lemkul2016},
2) the induced point dipole/multipole, Atomic Multipole Optimized Energetics for BiomoleculAr (AMOEBA), uses polarizable point dipoles placed on chosen sites of the molecule~\cite{ponder2010current},
and 3) the electronegativity equilization (FQ) employs atomic charges that are no longer constant but can change (redistribute within the molecule) according to the electronegativities of the molecule atoms and the electric fields from the molecular environment~\cite{patel2004charmm}. All of these approaches result in an increasing computational cost, e.g, by introducing new types of interactions, more interactions sites, or by requiring a shorter time step in the simulations. As an alternative approach, electronic continuum correction (ECC) has been proposed as a computational efficient method to implicitly include polarizability by scaling the atom partial charges~\cite{Melcr:2018a,dijon20}.

Our previous efforts in benchmarking state-of-the-art non-polarizable lipid force fields have demonstrated that the quality of predictions for important membrane properties greatly vary between different force fields, particularly for lipid headgroup conformational ensembles and ion binding affinities~\cite{Botan2015,Catte2016,Antila2019,bacle21,Antila2021,Antila2022,Databank}. The ability to capture these membrane properties correctly is important on its own but also creates the basis for the description of more complex systems: for example, ion binding affinity regulates membrane surface charge and having wide variety of conformations available for lipid headgroups appears to be important for capturing realistic protein-lipid interactions~\cite{bacle21}. Therefore, such benchmark studies are urgently needed also for polarizable lipid force fields, considering  the increased computational cost they come with, and most importantly, their pledge
%important when employing polarizable force fields, as they offer the potential 
to capture a broader range of physical phenomena pertinent to enhancing our understanding of in particular polar membrane regions.

Here we assess the quality of the actively developed polarizable lipid force fields, CHARMM-Drude~\cite{li2017drude,yu2023drude} and  AMOEBA-based~\cite{chu2018anionicpolarizable,chu2018polarizable} parameters, using the resources and the framework from the NMRlipids open collaboration (\url{http://nmrlipids.blogspot.fi/}). These two force fields were selected for comparison because they are increasingly utilized in biomolecular simulations and have parameters available for several lipids for which corresponding experimental data is available in NMRlipids databank~\cite{Databank}. We assess the structural quality of POPC, DOPC and POPE lipid bilayer simulations against experimental NMR and small angle X-ray scattering (SAXS) data using the quality metrics defined in the NMRlipids databank~\cite{Databank}. Cation binding to membranes is evaluated against salt-induced changes NMR order parameters~\cite{Catte2016} and lipid conformational dynamics is benchmarked to data from NMR spin relaxation rate experiments~\cite{ferreira15,Antila2021}. 
Furthermore, for each experimental benchmark we compare the results from polarizable models to those from the best performing non-polarizable simulations obtained from the NMRlipids Databank\cite{Databank}. Our results will act as a useful reference for selecting the best polarizable lipid models for wide range of applications and for guiding the development of polarizable force field parameters for lipids.

\section{Methods}

\subsection{Using a polarizable force field for membrane simulations}

While non-polarizable MD simulations of membranes can be nowadays routinely performed with several simulation packages and force fields, polarizable simulations bear many practical complications.
%Secondly, there are compability issues with the most used MD engines and the polarizable models and that support might be version dependent. 
Out of the currently popular MD simulation packages for membrane simulations, OpenMM~\cite{eastman2017openmm} supports both AMOEBA and Drude force fields, NAMD~\cite{phillips2020scalable} can only run the Drude force field, whereas GROMACS~\cite{abraham2015gromacs}
%---the most popular MD engine within the bilayer simulation field---
has only limited support for the Drude polarizable force field via an unofficial Git-branch~\cite{drudegithub}.  
TINKER is widely used with AMOEBA, but it does not support semi-isotropic pressure coupling, which %decouples the pressure tensor in $xy$ and $z$-direction and is 
is required in membrane simulations.%~\cite{xxx}.
%crucial for correctly modelling membrane systems~\cite{xxx}.
%
Consequently, we have selected OpenMM for simulations in this work.
%In general, easy access to MD engines, as well as adaptability of common analysis tools and libraries for polarizable force fields, will be crucial in facilitating more wide-spread utilization of these models.

Another practical issue is availability of parameters for the molecules of interest. CHARMM-GUI can generate the topology and input parameters for the Drude force field, which greatly simplifies the employment of this model in particular~\cite{kognole2022charmm}. Standard protocols for AMOEBA lipid parameters are not available, but some parameters can be found online~\cite{amoebagithub,klesse2020induced}.

%Considering the increased interest in polarizable force fields in membrane simulations, we mention here some hurdles in their practical usage. Firstly, 
Lastly, while conducting polarizable membrane simulations, one should consider the increased computational cost arising from the explicit treatment of electronic polarizability. For the Drude-based models, this slowdown occurs both because the addition of the Drude particles increases the number of interaction pairs and the employed extended dual-Langevin thermostat requires a shorter 1~fs integration time step, compared to the 2~fs typically used for non-polarizable membrane simulations. The AMOEBA force field can use a multi time-step integration algorithm where the non-electronic interactions are iterated with a 2~fs time step whereas more computationally unstable polarization terms are iterated with a smaller time step. However, the multi-time step scheme  only partly mitigates the computational cost: one typically experiences almost a ten-fold decrease in the simulation speed while using the polarizable force fields.

CHARMM-Drude2017 simulations were performed with OpenMM 7.5.0~\cite{eastman2017openmm} using parameters extracted with \textit{Membrane Builder}~\cite{wu2014charmm,jo2009charmm,jo2007automated,lee2018charmm} and \textit{Drude Prepper}~\cite{kognole2022charmm} from CHARMM-GUI~\cite{jo2008charmm,lee2016charmm}. Before starting the simulations, membrane structures were equilibrated for 200~ns using the non-polarizable CHARMM36 force field~\cite{klauda2010update}, and the last frames of these simulations were used to generate the starting structures for the polarizable force field simulations. Ion parameters are obtained from Ref.~\citenum{lin2018polarizable} and SWM4-NDP water model is employed in all Drude simulations~\cite{lamoureux2006polarizable}.

CHARMM-Drude2023 force field parameters are currently not integrated into CHARMM-GUI. Therefore, the simulation setups with NaCl and CaCl$_{2}$~\cite{lin2018polarizable} using SWM4-NDP water model~\cite{lamoureux2006polarizable} have been generated following the instructions in the original CHARMM-Drude2023 paper~\cite{yu2023drude} using CHARMM program~\cite{brooks2009charmm} and the last frame of 200~ns long CHARMM36 simulations (same for CHARMM-Drude2017). The salt-free CHARMM-Drude2023 simulations were obtained from Zenodo~\cite{richard_m_venable_2023_7872447, richard_m_venable_2023_7871949}.

A dual Langevin thermostat was employed to keep the Drude particles and the rest of the system at 1.0~K and 303~K, respectively. A Drude-hardwall of 0.02~nm was utilized to keep the Drude particles close to their parent atoms. Semi-isotropic Monte Carlo barostat was used to couple pressure to 1~bar independently in membrane plane and normal directions. %while the pressure fluctuations along the $xy$-plane were coupled. A constant surface tension of 0.0~dyne/cm was applied throughout the simulations. 
Bonds containing the hydrogens were constrained. For CHARMM-Drude2017, particle mesh Ewald was used to compute the Coulomb interactions and Van der Waals interactions were set to 0 between 1.0~nm and 1.2~nm using a switching function. For the CHARMM-Drude2023, Lennard-Jones particle-mesh Ewald (LJ-PME) method was used to compute the long-range dispersions~\cite{wennberg2013lennard}. Simulation frames were saved in every 10~ps.

\subsection{Simulations with AMOEBA-based parameters}

For simulations with the AMOEBA-based force field, we used the OpenMM implementation of parameters developed by Chu \textit{et al.}~\cite{chu2018polarizable} available at GitHub~\cite{amoebagithub,klesse2020induced}. All AMOEBA simulations were run using OpenMM 7.1.1~\cite{eastman2017openmm}. The same initial structures as in CHARMM-Drude simulations were used. A multi-time step Langevin integrator was used to iterate the bonded and non-bonded interactions in every 0.5~fs and 2.0~fs, respectively. A non-bonded cutoff of 1.2~nm was applied while semi-isotropic Monte Carlo barostat was used to couple pressure to 1~bar independently in membrane plane and normal directions. Ion and water parameters were obtained from Ref.~\citenum{shi2013proteinamoeba}.
%keeping the pressure at 1~bar using a Monte Carlo barostat. Pressure fluctuations in the $xy$-plane has been coupled using a semi-isotropic pressure coupling and a constant surface tension at 0.0~dyn/cm has been applied throughout the simulations. 
Simulation frames were saved in every 10~ps. Further simulations details can be found in the input files of the respective simulations (Table~\ref{table:sim_details}).

\subsection{Analysis of simulations}
All simulations were first uploaded to the NMRlipids databank~\cite{Databank}. Area per lipids, small angle X-ray scattering form factors, and order parameters ($S_{CH}$) are automatically calculated by the NMRlipids Databank~\cite{Databank} and were extracted from therein. Quality evaluation metrics were quantified as detailed in the NMRlipids databank~\cite{Databank} with the exception that POPC simulations at 303\,K were paired with the experimental data measured at 300\,K, while in the NMRlipids databank simulations are paired with experiments with the maximum temperature difference of two degrees. The order parameter qualities, $P^{\mathrm{headgroup}}$, $P^{sn-1}$, and $P^{sn-2}$, presents an average probability for order parameters of a given segment to locate within experimental values, taking the error bars of both values into account. Qualities of SAXS form factors, $FF_{q}$, depict the distance of the first form factor minima between simulation and experiment. This avoids the effects from the simulation size dependency of the SAXS data~\cite{Databank}.
%~\cite{Databank} one should focus on the extrema $q_{z}$[\AA$^{-1}$] when comparing the simulated and experimental data. In particular $FFq$ only measures the difference between the first minima of the simulated and experimental curves. 
Note that in quantifying the bilayer electron densities for calculation of SAXS curves, the NMRlipids databank analysis algorithm places electrons as point charges at the atom centers without considering redistribution of charge density due to the polarizability. Nevertheless, we expect this approximation not to have significant effect on the resulting SAXS form factors.

The density profiles were calculated using  MDAnalysis~\cite{michaud2011mdanalysis,gowers2016mdanalysis}/NumPy~\cite{harris2020array} for CHARMM-Drude and AMOEBA simulations, and 
\textit{gmx density} command from Gromacs package for the CHARMM36 and ECClipids simulations, for which the trajectories where extracted from the NMRlipids databank. In all calculations, the center of mass of the system is translated to origin coordinates. All data is normalized such that the area under the curve is equal to unity. The $R_{1}$ rates and effective correlation times, along with the accompanying error estimates, were quantified from the trajectories as elaborated in Ref.~\citenum{Antila2021}. In-house python script available at \url{https://github.com/NMRLipids/NMRlipidsVIpolarizableFFs/tree/master/scripts/correlation_times} was used for this purpose.

%\newpage
%\begin{adjustbox}{angle=90}
\begin{table}[ht!]
\begin{small}
\begin{tabular}{cccccccccc}
	Lipid/ion                & force field  & Ion (M) & N$_{l}$ & N$_{w}$ & N$_{ion}$ & T (K) & t$_{sim}$ (ns) & t$_{analysis}$ (ns) & files [Ref.]\\ \hline
\multirow{2}{*}{POPC}            & Drude2017 & 0      & 144       & 6400       & 0         & 303    & 500              & 400         &          \citenum{kav_batuhan_2021_7607436}    \\ 
                                 & Drude2023 & 0      & 72       & 2239       & 0         & 303      & 300              & 200         &          \citenum{kav_batuhan_2023_7916287}, \citenum{richard_m_venable_2023_7871949}    \\ \hline
\multirow{3}{*}{POPE}                              & Drude2017 & 0      & 144       & 6400       & 0         & 308.15    & 350              & 300         &          \citenum{kav_batuhan_2021_7604627}    \\                                            & Drude2023 & 0       & 72        & 2304      &  0         & 303    & 300             & 200         &           \citenum{richard_m_venable_2023_7872447}, \citenum{kav_batuhan_2023_7916494} \\
                                                  & AMOEBA     & 0       & 72        & 2880      &  0        & 303     & 305.94          & 305.94      & \citenum{kav_batuhan_2023_7622838} \\ \hline
	\multirow{5}{*}{POPC:NaCl}        & Drude2017 & 0.350   & 144      & 6400     & 41         & 303   & 500             & 400                  & \citenum{kav_batuhan_2020_7586915}   \\
				  & Drude2017 & 0.450   & 144      & 6400     & 51         & 303   & 500             & 400                  & \citenum{kav_batuhan_2020_7591753}   \\
				  & Drude2017 & 0.650   & 144      & 6400     & 77         & 303   & 500             & 400                  & \citenum{kav_batuhan_2020_7596011}   \\
				  & Drude2017 & 1.0     & 144      & 6400     & 115        & 303   & 500             & 400                  & \citenum{kav_batuhan_2020_7600326}   \\ 
                    & Drude2023 & 0.350      & 128       & 6400      & 41          & 303    & 223.97      &       220.14       & \citenum{kav_batuhan_2023_8000095} \\     
                    & Drude2023 & 1.0      & 128       & 6400      & 115          & 303    & 220.14      &       220.14       & \citenum{kav_batuhan_2023_8000133} \\ \hline

	\multirow{5}{*}{POPC:CaCl$_{2}$} & Drude2017 & 0.350   & 144      & 6400     & 41         & 303   & 500             & 400                  & \citenum{kav_batuhan_2020_7600827}   \\
				  & Drude2017 & 0.450   & 144      & 6400     & 52         & 303   & 500             & 400                  & \citenum{kav_batuhan_2020_7605016}   \\
				  & Drude2017 & 0.650   & 144      & 6400     & 76         & 303   & 500             & 400                  & \citenum{kav_batuhan_2020_7604040} \\
				  & Drude2017 & 1.0   & 144      & 6400     & 114         & 303   & 500             & 400                  & \citenum{kav_batuhan_2023_7658975}\\
                    & Drude2023 & 0.350 & 128      & 6400     & 41          & 303   & 219.59          & 219.59               & \citenum{kav_batuhan_2023_8000065}\\
                    & Drude2023 & 0.790 & 128      & 6400     & 91          & 303   & 214.85          & 214.85               & \citenum{kav_batuhan_2023_7992137} \\ \hline
DOPC           & AMOEBA   & 0 & 72 & 2880 & 0 & 303 & 201.61 & 201.61 & \citenum{kav_batuhan_2022_7604681} \\ \hline
\multirow{2}{*}{DOPC:NaCl} & AMOEBA & 0.450 & 72 & 2880 & 17 & 303 & 218.41 & 218.41 & \citenum{kav_batuhan_2022_7604711} \\
                           & AMOEBA & 1.0 & 72 & 2880 &  35 & 303 & 201.61 & 201.61 & \citenum{kav_batuhan_2023_7625844} \\ \hline
\multirow{2}{*}{DOPC:CaCl$_{2}$} & AMOEBA  & 0.450 & 72 & 2880 & 16 & 303 & 218.41 & 218.41 & \citenum{kav_batuhan_2022_7604842} \\
                                 & AMOEBA & 1.0 & 72 & 2880  & 36 & 303 & 218.41 & 218.41 & \citenum{kav_batuhan_2022_7604810}

\end{tabular}
\end{small}
\caption{Systems simulated for this work. Column N$_l$ gives the number of lipids, N$_w$ gives the number of water molecules, T(K) denotes the temperature in kelvins. Simulated time is listed in column t$_{sim}$ and time used for analysis in t$_{analysis}$. Column "files" gives the reference to open access simulation data. The salt concentrations calculated as [salt]=N$_c$×[water] / N$_w$, where [water] = 55.5 M}
\label{table:sim_details}
\end{table}
\todo{check the simualation settings (especially the temperature}

@@

To evaluate the structural properties of lipid bilayers in simulations with polarizable force fields, we simulated POPC and POPE lipid bilayers with CHARMM-Drude2017~\cite{li2017drude} and CHARMM-Drude2023~\cite{yu2023drude} parameters, and POPE and DOPC bilayers with AMOEBA-based~\cite{chu2018anionicpolarizable,chu2018polarizable} parameters. These systems were selected based on simultaneous availability of force field parameters and experimental data~\cite{Databank}. After the data production, simulation trajectories were added into the NMRlipids Databank and its quality metric were used to evaluate each simulation against experiments~\cite{Databank}. The metric measures the quality of lipid bilayer simulations in two aspects: first, it evaluates the quality of conformational ensemble of individual lipids against C-H bond order parameters from NMR, and second, it examines consistency of membrane dimensions compared to small angle X-ray scattering  data~\cite{Databank,ollila16}. 
The former is divided into three parts that separately describe the average quality of headgroup, glycerol backbone and acyl chain regions. While order parameters primarily reflect lipid conformations, acyl chain order parameters are also a good proxy for membrane packing since a smaller area per lipid tends to increase the magnitude of the order parameters~\cite{Databank}. 
%one for each of the carbonyl tails, and the quality of each is evaluated separately.

%\begin{figure}[t]
%    \centering
    %\includegraphics{Figures/order_parameters.png}
    %\includegraphics[width=0.4\textwidth]{Figures/molecules.pdf}
    %\caption{Molecules and atom labelling used.}
%    \label{fig:molecules}
%
%\end{figure}

\begin{figure}[!p]
    \centering
    %\includegraphics{Figures/order_parameters.png}
    \includegraphics[width=0.9\textwidth]{Figures/quality.pdf}
    \caption{X-ray scattering form factors, and C-H bond order parameters for headgroup and glycerol backbone, and acyl chains (from top to bottom) compared between simulations and experiments using the NMRlipids databank. Experimental data in this figure are originally reported in Refs.~\citenum{ferreira13,bacle21,Databank,NMRlipidsIII,kucerka2015}. For CHARMM-Drude2023 simulations we selected representative replicas among three available one (for all POPC replicas, see SI Fig. S1). Right most panel shows the modelled lipids and the used carbon naming scheme.}
    \label{fig:order_parameters}

@@
